Investigating the influence of genre preferences on movie/series rating patterns over time

### 2024-03-18 gen/paper/paper.Rmd
wrote the results section

## Results

@@

git mv old_file.txt new_file.txt
git commit -m "Rename file from old_file.txt to new_file.txt"

>>>>

## Results
The results indicated that there are different genre preferences over time.
Out of all twenty five genres, only aighteen appeared to significantly influence the average ratings on IMBd. These genres were animation, biography, film-noir, fanatsy, documentary, crime, comedy, game-show, history, horror, musical, shorts, sci-fi, romance, reality-tv, news, and war.

The genre history fell in favor in around the year 1960 and continued to significantly (p~1960<.01) influence the average rating until this day.

@@
